Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Our argument now proceeds to prove the ``if direction'': assuming $h \in \dcross_H(\bm{t})$, we aim to show $h \in \cross_H(r^*)$. Recall that $r^* = [x_1,x_2] \times [y_1, \maxtop(r')]$. To prove that $h$ crosses $r^*$, we will show $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$, where $y_h$ is the y-coordinate of $h$.
\myitems{
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $r'$. As $[x_1, x_2]$ is the x-range of $r'$, we know $\xleft(h) < x_1 \le x_2 < \xright(h)$.

>>>>

We now proceed to establish the ``if direction'': assuming $h \in \dcross_H(\bm{t})$, we aim to show $h \in \cross_H(r^*)$. Recall that $r^* = [x_1,x_2] \times [y_1, \maxtop(r')]$. To prove that $h$ crosses $r^*$, we will argue that $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$, where $y_h$ is the y-coordinate of $h$.
\myitems{
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $r'$. As $[x_1, x_2]$ is the x-range of $r'$, we know $\xleft(h) < x_1 \le x_2 < \xright(h)$.
